Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Implementation introduction

\section{Implementation \tbr}
\label{sec:implementation}

A Spanner deployment is referred to as a \emph{universe} which consists of
multiple zones. A universe has two global components: A \emph{universemaster}
which, essentially, is a debugging console and shows the status of each zone. A
\emph{placement driver} which automatically moves data between zones due to
modified replication constraints or load balancing between zones.

@@

According to Google, a zone can be seen as a Bigtable server deployment. The set
of zones also determines the locations across which the data can be replicated.
One can also think of a zone as geographically wide-spread locations, e.g.
continents. Using such a physical isolation, Spanner is resistent to events which
affect large areas, e.g. natural disasters or war. Hence, a well-configured
Spanner deployment is available almost all the time.
Figure~\ref{subfig:spanner-universe} illustrates the organization of a Spanner
universe.

>>>>

\section{Implementation}
\label{sec:implementation}

A Spanner deployment is referred to as a \emph{universe} which consists of
multiple zones. A universe has two global components: A \emph{universemaster}
which is a debugging console and shows the status of each zone. A
\emph{placement driver} which automatically moves data between zones due to
modified replication constraints or load balancing between zones.

@@

According to Google, a zone can be seen as a Bigtable server deployment. The set
of zones also determines the locations across which the data can be replicated.
One can also think of a zone as geographically wide-spread locations, e.g.
continents. Using this kind of physical isolation, Spanner is resistent to events
which affect large areas, e.g. natural disasters or war. Hence, a well-configured
Spanner deployment is available almost all the time.
Figure~\ref{subfig:spanner-universe} illustrates the organization of a Spanner
universe.
